Observed vs. Simulated Year Comparison

### 2023-02-28 03-post-process/compare-sim-to-obs.Rmd
Fix small typo in sim-v-obs rmd
Improve memory usage of post-MCMC calculations
Sim-v-obs compares many derived quantities that are not monitored via mcmc. The old code was super memory heavy, this code is (much) faster and take less memory

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output:
   html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
editor_options: 
  chunk_output_type: console
---

@@

o_nor = 1   # o = 1 is NOR
o_hor = 2   # o = 2 is HOR
k_3 = 1     # k = 1 is age-3
k_4 = 2     # k = 2 is age-4
k_5 = 3     # k = 3 is age-5
j_cat = 1   # j = 1 is CAT
j_los = 2   # j = 2 is LOS
j_min = 3   # j = 3 is MIN
j_ugr = 4   # j = 4 is UGR
```

@@

```{r add-p-hos}
# extract spawners returning to tributary
Ra = post_subset(post, "^Ra[", matrix = TRUE)

# for each posterior sample, calculate the fraction that are hatchery origin
out = NULL
for (i in 1:nrow(Ra)) {
  Ra_i = array_format(Ra[i,])
  nor = Ra_i[,1,1,] + Ra_i[,2,1,] + Ra_i[,3,1,]
  hor = Ra_i[,1,2,] + Ra_i[,2,2,] + Ra_i[,3,2,]
  out = rbind(out, as.numeric(hor/(nor + hor)))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(nor), ncol(nor))

# build the column indices for each element: the population
c_ind = rep(1:ncol(nor), each = nrow(nor))

# make element names
colnames(out) = paste0("p_hor[", r_ind, ",", c_ind, "]")

# drop out those that have NA values (first k_max years)
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-p-hos-age}
# extract spawners returning to tributary
Ra = post_subset(post, "^Ra[", matrix = TRUE)

# for each posterior sample, calculate the fraction that are hatchery origin
out_3 = out_4 = out_5 = NULL
for (i in 1:nrow(Ra)) {
  Ra_i = array_format(Ra[i,])

  p_hor_3 = Ra_i[,k_3,o_hor,]/(Ra_i[,k_3,o_nor,] + Ra_i[,k_3,o_hor,])
  p_hor_4 = Ra_i[,k_4,o_hor,]/(Ra_i[,k_4,o_nor,] + Ra_i[,k_4,o_hor,])
  p_hor_5 = Ra_i[,k_5,o_hor,]/(Ra_i[,k_5,o_nor,] + Ra_i[,k_5,o_hor,])

  out_3 = rbind(out_3, as.numeric(p_hor_3))
  out_4 = rbind(out_4, as.numeric(p_hor_4))
  out_5 = rbind(out_5, as.numeric(p_hor_5))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(p_hor_3), ncol(p_hor_3))

# build the column indices for each element: the population
c_ind = rep(1:ncol(p_hor_3), each = nrow(p_hor_3))

# make element names
colnames(out_3) = paste0("p_hor_a[", r_ind, ",1,", c_ind, "]")
colnames(out_4) = paste0("p_hor_a[", r_ind, ",2,", c_ind, "]")
colnames(out_5) = paste0("p_hor_a[", r_ind, ",3,", c_ind, "]")
out = cbind(out_3, out_4, out_5)

# drop out those that have NA values (first k_max years)
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-Rb-tot-origin}
# extract returns to estuary
Rb = post_subset(post, "^Rb[", matrix = TRUE)

# for each posterior sample, calculate the abundance by origin and total
out_tot = out_nor = out_hor = NULL
for (i in 1:nrow(Rb)) {
  Rb_i = array_format(Rb[i,])
  nor = Rb_i[,1,1,] + Rb_i[,2,1,] + Rb_i[,3,1,]
  hor = Rb_i[,1,2,] + Rb_i[,2,2,] + Rb_i[,3,2,]
  tot = nor + hor

  out_nor = rbind(out_nor, as.numeric(nor))
  out_hor = rbind(out_hor, as.numeric(hor))
  out_tot = rbind(out_tot, as.numeric(tot))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(nor), ncol(nor))

# build the column indices for each element: the population
c_ind = rep(1:ncol(nor), each = nrow(nor))

# make element names
colnames(out_nor) = paste0("Rb_tot_org[", r_ind, ",1,", c_ind, "]")
colnames(out_hor) = paste0("Rb_tot_org[", r_ind, ",2,", c_ind, "]")
colnames(out_tot) = paste0("Rb_tot[", r_ind, ",", c_ind, "]")
out = cbind(out_nor, out_hor, out_tot)

# drop out those that have NA values (first k_max years)
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-Ra-tot-origin}
# extract returns to tributary
Ra = post_subset(post, "^Ra[", matrix = TRUE)

# for each posterior sample, calculate the abundance by origin and total
out_nor = out_hor = NULL
for (i in 1:nrow(Ra)) {
  Ra_i = array_format(Ra[i,])
  nor = Ra_i[,1,1,] + Ra_i[,2,1,] + Ra_i[,3,1,]
  hor = Ra_i[,1,2,] + Ra_i[,2,2,] + Ra_i[,3,2,]

  out_nor = rbind(out_nor, as.numeric(nor))
  out_hor = rbind(out_hor, as.numeric(hor))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(nor), ncol(nor))

# build the column indices for each element: the population
c_ind = rep(1:ncol(nor), each = nrow(nor))

# make element names
colnames(out_nor) = paste0("Ra_tot_org[", r_ind, ",1,", c_ind, "]")
colnames(out_hor) = paste0("Ra_tot_org[", r_ind, ",2,", c_ind, "]")
out = cbind(out_nor, out_hor)

# drop out those that have NA values (first k_max years)
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-Sa-tot-origin}
# extract spawners
Sa = post_subset(post, "^Sa[", matrix = TRUE)

# for each posterior sample, calculate the abundance by origin and total
out_nor = out_hor = NULL
for (i in 1:nrow(Ra)) {
  Sa_i = array_format(Sa[i,])
  nor = Sa_i[,1,1,] + Sa_i[,2,1,] + Sa_i[,3,1,]
  hor = Sa_i[,1,2,] + Sa_i[,2,2,] + Sa_i[,3,2,]

  out_nor = rbind(out_nor, as.numeric(nor))
  out_hor = rbind(out_hor, as.numeric(hor))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(nor), ncol(nor))

# build the column indices for each element: the population
c_ind = rep(1:ncol(nor), each = nrow(nor))

# make element names
colnames(out_nor) = paste0("Sa_tot_org[", r_ind, ",1,", c_ind, "]")
colnames(out_hor) = paste0("Sa_tot_org[", r_ind, ",2,", c_ind, "]")
out = cbind(out_nor, out_hor)

# drop out those that have NA values (first k_max years)
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-E-origin}
E = post_subset(post, "^E_sep[", matrix = TRUE)

out_nor = out_hor = NULL
for (i in 1:nrow(Ra)) {
  E_i = array_format(E[i,])
  E_nor_i = E_i[,1,1,] + E_i[,2,1,] + E_i[,3,1,]
  E_hor_i = E_i[,1,2,] + E_i[,2,2,] + E_i[,3,2,]

  out_nor = rbind(out_nor, as.numeric(E_nor_i))
  out_hor = rbind(out_hor, as.numeric(E_hor_i))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(nor), ncol(nor))

# build the column indices for each element: the population
c_ind = rep(1:ncol(nor), each = nrow(nor))

# make element names
colnames(out_nor) = paste0("E_org[", r_ind, ",1,", c_ind, "]")
colnames(out_hor) = paste0("E_org[", r_ind, ",2,", c_ind, "]")
out = cbind(out_nor, out_hor)

# drop out those that have NA values (first k_max years)
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-E-per-Sa-origin}
Sa = post_subset(post, "^Sa[", matrix = TRUE)
E = post_subset(post, "^E_sep[", matrix = TRUE)

out_nor = out_hor = NULL
for (i in 1:nrow(Ra)) {
  Sa_i = array_format(Sa[i,])
  Sa_nor_i = Sa_i[,1,1,] + Sa_i[,2,1,] + Sa_i[,3,1,]
  Sa_hor_i = Sa_i[,1,2,] + Sa_i[,2,2,] + Sa_i[,3,2,]
  E_i = array_format(E[i,])
  E_nor_i = E_i[,1,1,] + E_i[,2,1,] + E_i[,3,1,]
  E_hor_i = E_i[,1,2,] + E_i[,2,2,] + E_i[,3,2,]

  out_nor = rbind(out_nor, as.numeric(E_nor_i/Sa_nor_i))
  out_hor = rbind(out_hor, as.numeric(E_hor_i/Sa_hor_i))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(nor), ncol(nor))

# build the column indices for each element: the population
c_ind = rep(1:ncol(nor), each = nrow(nor))

# make element names
colnames(out_nor) = paste0("E_per_Sa_org[", r_ind, ",1,", c_ind, "]")
colnames(out_hor) = paste0("E_per_Sa_org[", r_ind, ",2,", c_ind, "]")
out = cbind(out_nor, out_hor)

# drop out those that have NA values (first k_max years)
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-Ma-tot}
# extract smolt at LGR
Ma = post_subset(post, "^Ma[", matrix = TRUE)

# for each posterior sample, calculate the number of NOR and HOR smolt at LGR
out_nor = NULL
out_hor = NULL
for (i in 1:nrow(Ma)) {
  Ma_i = array_format(Ma[i,])
  nor = Ma_i[,1,1,] + Ma_i[,2,1,]
  hor = Ma_i[,2,2,]
  out_nor = rbind(out_nor, as.numeric(nor))
  out_hor = rbind(out_hor, as.numeric(hor))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(nor), ncol(nor))

# build the column indices for each element: the population
c_ind = rep(1:ncol(nor), each = nrow(nor))

# make element names
colnames(out_nor) = paste0("Ma_tot[", r_ind, ",", "1", ",", c_ind, "]")
colnames(out_hor) = paste0("Ma_tot[", r_ind, ",", "2", ",", c_ind, "]")
out = cbind(out_nor, out_hor)

# drop out those that have NA values (first k_max years)
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-age-comp}
Ra = post_subset(post, "^Ra[", matrix = TRUE)

# for each posterior sample, calculate the fraction that of each age by origin
p3_nor_out = p4_nor_out = p5_nor_out = p3_hor_out = p4_hor_out = p5_hor_out = NULL
for (i in 1:nrow(Ra)) {
  Ra_i = array_format(Ra[i,])
  nor_tot = Ra_i[,1,1,] + Ra_i[,2,1,] + Ra_i[,3,1,]
  hor_tot = Ra_i[,1,2,] + Ra_i[,2,2,] + Ra_i[,3,2,]

  p3_nor = Ra_i[,1,1,]/nor_tot
  p4_nor = Ra_i[,2,1,]/nor_tot
  p5_nor = Ra_i[,3,1,]/nor_tot
  p3_hor = Ra_i[,1,2,]/hor_tot
  p4_hor = Ra_i[,2,2,]/hor_tot
  p5_hor = Ra_i[,3,2,]/hor_tot

  p3_nor_out = rbind(p3_nor_out, as.numeric(p3_nor))
  p4_nor_out = rbind(p4_nor_out, as.numeric(p4_nor))
  p5_nor_out = rbind(p5_nor_out, as.numeric(p5_nor))
  p3_hor_out = rbind(p3_hor_out, as.numeric(p3_hor))
  p4_hor_out = rbind(p4_hor_out, as.numeric(p4_hor))
  p5_hor_out = rbind(p5_hor_out, as.numeric(p5_hor))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(p3_nor), ncol(p3_nor))

# build the column indices for each element: the population
c_ind = rep(1:ncol(p3_nor), each = nrow(p3_nor))

# make element names
colnames(p3_nor_out) = paste0("Ra_comp[", r_ind, ",", "1", ",", "1", ",", c_ind, "]")
colnames(p4_nor_out) = paste0("Ra_comp[", r_ind, ",", "2", ",", "1", ",", c_ind, "]")
colnames(p5_nor_out) = paste0("Ra_comp[", r_ind, ",", "3", ",", "1", ",", c_ind, "]")
colnames(p3_hor_out) = paste0("Ra_comp[", r_ind, ",", "1", ",", "2", ",", c_ind, "]")
colnames(p4_hor_out) = paste0("Ra_comp[", r_ind, ",", "2", ",", "2", ",", c_ind, "]")
colnames(p5_hor_out) = paste0("Ra_comp[", r_ind, ",", "3", ",", "2", ",", c_ind, "]")

out = cbind(p3_nor_out, p4_nor_out, p5_nor_out, p3_hor_out, p4_hor_out, p5_hor_out)

# drop out those that have NA values (first k_max years)
out[out == "NaN"] = 0
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-age-comp-combined}
Ra = post_subset(post, "^Ra[", matrix = TRUE)

p3_out = p4_out = p5_out = NULL
for (i in 1:nrow(Ra)) {
  Ra_i = array_format(Ra[i,])

  a3_tot = Ra_i[,1,1,] + Ra_i[,1,2,]
  a4_tot = Ra_i[,2,1,] + Ra_i[,2,2,]
  a5_tot = Ra_i[,3,1,] + Ra_i[,3,2,]
  tot = a3_tot + a4_tot + a5_tot

  p3 = Ra_i[,1,1,]/tot
  p4 = Ra_i[,2,1,]/tot
  p5 = Ra_i[,3,1,]/nor_tot

  p3_out = rbind(p3_out, as.numeric(p3))
  p4_out = rbind(p4_out, as.numeric(p4))
  p5_out = rbind(p5_out, as.numeric(p5))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(p3), ncol(p3))

# build the column indices for each element: the population
c_ind = rep(1:ncol(p3), each = nrow(p3))

# make element names
colnames(p3_out) = paste0("Ra_comp_a[", r_ind, ",", "1", ",", c_ind, "]")
colnames(p4_out) = paste0("Ra_comp_a[", r_ind, ",", "2", ",", c_ind, "]")
colnames(p5_out) = paste0("Ra_comp_a[", r_ind, ",", "3", ",", c_ind, "]")

out = cbind(p3_out, p4_out, p5_out)

# drop out those that have NA values (first k_max years)
out[out == "NaN"] = 0
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-trib-smolt-per-parr}
Mb = post_subset(post, "^Mb[", matrix = TRUE)
Pa = post_subset(post, "^Pa[", matrix = TRUE)

# for each posterior sample, calculate survival from parr to lgr smolt by LH type
out_fall = out_spring = NULL

for (i in 1:nrow(Mb)) {
  Mb_i = array_format(Mb[i,])
  Pa_i = array_format(Pa[i,])

  Mb_per_Pa = Mb_i[,,1,]/Pa_i

  out_fall = rbind(out_fall, as.numeric(Mb_per_Pa[,1,]))
  out_spring = rbind(out_spring, as.numeric(Mb_per_Pa[,2,]))
}

# build the row indices for each element: the year
r_ind = rep(1:dim(Mb_per_Pa)[1], dim(Mb_per_Pa)[3])

# build the column indices for each element: the population
c_ind = rep(1:dim(Mb_per_Pa)[3], each = dim(Mb_per_Pa)[1])

# make element names
colnames(out_fall) = paste0("Mb_per_Pa[", r_ind, ",", "1", ",", c_ind, "]")
colnames(out_spring) = paste0("Mb_per_Pa[", r_ind, ",", "2", ",", c_ind, "]")

out = cbind(out_fall, out_spring)

# drop out those that have NA values (first k_max years)
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-lgr-smolt-per-parr}
Ma = post_subset(post, "^Ma[", matrix = TRUE)
Pa = post_subset(post, "^Pa[", matrix = TRUE)

# for each posterior sample, calculate survival from parr to lgr smolt by LH type
out_fall = out_spring = NULL

>>>>

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output:
   html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "tack-on-all-priors"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 0.5
    input: numeric
editor_options: 
  chunk_output_type: console
---

@@

o_nor = 1     # o = 1 is NOR
o_hor = 2     # o = 2 is HOR
k_3 = 1       # k = 1 is age-3
k_4 = 2       # k = 2 is age-4
k_5 = 3       # k = 3 is age-5
j_cat = 1     # j = 1 is CAT
j_los = 2     # j = 2 is LOS
j_min = 3     # j = 3 is MIN
j_ugr = 4     # j = 4 is UGR
i_fall = 1    # i = 1 is fall migrants
i_spring = 2  # i = 2 is spring migrants

rm(model_info)
```

@@

```{r add-p-hos}
f = function() {
  # extract adults returning to tributary
  Ra = post_subset(post, "^Ra[", matrix = TRUE)

  # perform basic operations for one iteration -- for making dimension names later
  Ra_1 = array_format(Ra[1,])
  nor_1 = Ra_1[,k_3,o_nor,] + Ra_1[,k_4,o_nor,] + Ra_1[,k_5,o_nor,]

  # function to perform the calculation for one MCMC sample
  g = function(i) {
    Ra_i = array_format(Ra[i,])
    hor = Ra_i[,k_3,o_hor,] + Ra_i[,k_4,o_hor,] + Ra_i[,k_5,o_hor,]
    nor = Ra_i[,k_3,o_nor,] + Ra_i[,k_4,o_nor,] + Ra_i[,k_5,o_nor,]
    as.numeric(hor/(nor + hor))
  }

  # apply to each posterior sample
  out = t(sapply(1:nrow(Ra), g))

  # build element indices: the year
  y_ind = rep(1:nrow(nor_1), ncol(nor_1))

  # build element indices: the population
  j_ind = rep(1:ncol(nor_1), each = nrow(nor_1))

  # make element names
  colnames(out) = paste0("p_hor[", y_ind, ",", j_ind, "]")

  # drop out those that have NA values (first k_max years)
  na_ind = which(!is.na(out[1,]))
  out[,na_ind]
}

# combine with the rest of the posterior samples
post = post_bind(post, f()); rm(f)
```

```{r add-p-hos-age}
f = function() {
  # extract adults returning to tributary
  Ra = post_subset(post, "^Ra[", matrix = TRUE)

  # perform basic operations for one iteration -- for making dimension names later
  Ra_1 = array_format(Ra[1,])
  p_hor_3_1 = Ra_1[,k_3,o_hor,]/(Ra_1[,k_3,o_nor,] + Ra_1[,k_3,o_hor,])
  p_hor_4_1 = Ra_1[,k_4,o_hor,]/(Ra_1[,k_4,o_nor,] + Ra_1[,k_4,o_hor,])
  p_hor_5_1 = Ra_1[,k_5,o_hor,]/(Ra_1[,k_5,o_nor,] + Ra_1[,k_5,o_hor,])

  # function to perform the calculation for one MCMC sample
  g = function(i) {
    Ra_i = array_format(Ra[i,])
    p_hor_3 = Ra_i[,k_3,o_hor,]/(Ra_i[,k_3,o_nor,] + Ra_i[,k_3,o_hor,])
    p_hor_4 = Ra_i[,k_4,o_hor,]/(Ra_i[,k_4,o_nor,] + Ra_i[,k_4,o_hor,])
    p_hor_5 = Ra_i[,k_5,o_hor,]/(Ra_i[,k_5,o_nor,] + Ra_i[,k_5,o_hor,])
    c(as.numeric(p_hor_3), as.numeric(p_hor_4), as.numeric(p_hor_5))
  }

  # apply to each posterior sample
  out = t(sapply(1:nrow(Ra), g))

  # build element indices: the year
  y_ind = rep(rep(1:nrow(p_hor_3_1), ncol(p_hor_3_1)), 3)

  # build element indices: the population
  j_ind = rep(rep(1:ncol(p_hor_3_1), each = nrow(p_hor_3_1)), 3)

  # build element indices: the age
  k3_ind = rep(1, nrow(p_hor_3_1) * ncol(p_hor_3_1))
  k4_ind = rep(2, nrow(p_hor_3_1) * ncol(p_hor_3_1))
  k5_ind = rep(3, nrow(p_hor_3_1) * ncol(p_hor_3_1))
  k_ind = c(k3_ind, k4_ind, k5_ind)

  # build element names
  colnames(out) = paste0("p_hor_a[", y_ind, ",", k_ind, ",", j_ind, "]")

  # drop out those that have NA values
  na_ind = which(!is.na(out[1,]))
  out[,na_ind]
}

# combine this with the rest of the posterior samples
post = post_bind(post, f()); rm(f)
```

```{r add-Rb-tot-origin}
f = function() {
  # extract returns to estuary
  Rb = post_subset(post, "^Rb[", matrix = TRUE)

  # perform basic operations for one iteration -- for making dimension names later
  Rb_1 = array_format(Rb[1,])
  nor_1 = Rb_1[,k_3,o_nor,] + Rb_1[,k_4,o_nor,] + Rb_1[,k_5,o_nor,]
  hor_1 = Rb_1[,k_3,o_hor,] + Rb_1[,k_4,o_hor,] + Rb_1[,k_5,o_hor,]
  tot_1 = nor_1 + hor_1

  # function to perform the calculation for one MCMC sample
  g = function(i) {
    Rb_i = array_format(Rb[i,])
    nor = Rb_i[,k_3,o_nor,] + Rb_i[,k_4,o_nor,] + Rb_i[,k_5,o_nor,]
    hor = Rb_i[,k_3,o_hor,] + Rb_i[,k_4,o_hor,] + Rb_i[,k_5,o_hor,]
    tot = nor + hor

    list(nor = as.numeric(nor), hor = as.numeric(hor), tot = as.numeric(tot))
  }

  # apply to each posterior sample
  out = lapply(1:nrow(Rb), g)

  # convert these to their own matrices for easier element construction
  nor_out = do.call(rbind, lapply(out, function(x) x$nor))
  hor_out = do.call(rbind, lapply(out, function(x) x$hor))
  tot_out = do.call(rbind, lapply(out, function(x) x$tot))

  # build element indices: the year
  y_ind = rep(1:nrow(nor_1), ncol(nor_1))

  # build element indices: the population
  j_ind = rep(1:ncol(nor_1), each = nrow(nor_1))

  # build element names
  colnames(nor_out) = paste0("Rb_tot_org[", y_ind, ",", "1", ",", j_ind, "]")
  colnames(hor_out) = paste0("Rb_tot_org[", y_ind, ",", "2", ",", j_ind, "]")
  colnames(tot_out) = paste0("Rb_tot[", y_ind, ",", j_ind, "]")

  # combine matrices
  out = cbind(nor_out, hor_out, tot_out)

  # drop out those that have NA values
  na_ind = which(!is.na(out[1,]))
  out[,na_ind]
}

# combine with the rest of the posterior samples
post = post_bind(post, f()); rm(f)
```

```{r add-Ra-tot-origin}
f = function() {
  # extract returns to tributary
  Ra = post_subset(post, "^Ra[", matrix = TRUE)

  # perform basic operations for one iteration -- for making dimension names later
  Ra_1 = array_format(Ra[1,])
  nor_1 = Ra_1[,k_3,o_nor,] + Ra_1[,k_4,o_nor,] + Ra_1[,k_5,o_nor,]

  # function to perform the calculation for one MCMC sample
  g = function(i) {
    Ra_i = array_format(Ra[i,])
    list(
      nor = as.numeric(Ra_i[,k_3,o_nor,] + Ra_i[,k_4,o_nor,] + Ra_i[,k_5,o_nor,]),
      hor = as.numeric(Ra_i[,k_3,o_hor,] + Ra_i[,k_4,o_hor,] + Ra_i[,k_5,o_hor,])
    )
  }

  # apply to each posterior sample
  out = lapply(1:nrow(Ra), g)

  # convert these to their own matrices for easier element construction
  nor_out = do.call(rbind, lapply(out, function(x) x$nor))
  hor_out = do.call(rbind, lapply(out, function(x) x$hor))

  # build element indices: the year
  y_ind = rep(1:nrow(nor_1), ncol(nor_1))

  # build element indices: the population
  j_ind = rep(1:ncol(nor_1), each = nrow(nor_1))

  # build element names
  colnames(nor_out) = paste0("Ra_tot_org[", y_ind, ",", "1", ",", j_ind, "]")
  colnames(hor_out) = paste0("Ra_tot_org[", y_ind, ",", "2", ",", j_ind, "]")

  # combine
  out = cbind(nor_out, hor_out)

  # drop out those that have NA values
  na_ind = which(!is.na(out[1,]))
  out[,na_ind]
}

# combine with the rest of the posterior samples
post = post_bind(post, f()); rm(f)
```

```{r add-Sa-tot-origin}
f = function() {
  # extract posterior samples of spawners
  Sa = post_subset(post, "^Sa[", matrix = TRUE)

  # perform basic operations for one iteration -- for making dimension names later
  Sa_1 = array_format(Sa[1,])
  nor_1 = Sa_1[,k_3,o_nor,] + Sa_1[,k_4,o_nor,] + Sa_1[,k_5,o_nor,]
  hor_1 = Sa_1[,k_3,o_hor,] + Sa_1[,k_4,o_hor,] + Sa_1[,k_5,o_hor,]

  # function to perform the calculation for one MCMC sample
  g = function(i) {
    Sa_i = array_format(Sa[i,])
    list(
      nor = as.numeric(Sa_i[,k_3,o_nor,] + Sa_i[,k_4,o_nor,] + Sa_i[,k_5,o_nor,]),
      hor = as.numeric(Sa_i[,k_3,o_hor,] + Sa_i[,k_4,o_hor,] + Sa_i[,k_5,o_hor,])
    )
  }

  # apply to each posterior sample
  out = lapply(1:nrow(Sa), g)

  # convert these to their own matrices for easier element construction
  nor_out = do.call(rbind, lapply(out, function(x) x$nor))
  hor_out = do.call(rbind, lapply(out, function(x) x$hor))

  # build element indices: the year
  y_ind = rep(1:nrow(nor_1), ncol(nor_1))

  # build element indices: the population
  j_ind = rep(1:ncol(nor_1), each = nrow(nor_1))

  # build element names
  colnames(nor_out) = paste0("Sa_tot_org[", y_ind, ",", "1", ",", j_ind, "]")
  colnames(hor_out) = paste0("Sa_tot_org[", y_ind, ",", "2", ",", j_ind, "]")

  # combine
  out = cbind(nor_out, hor_out)

  # drop out those that have NA values
  na_ind = which(!is.na(out[1,]))
  out[,na_ind]
}

# combine with the rest of the posterior samples
post = post_bind(post, f()); rm(f)
```

```{r add-E-origin}
f = function() {
  # extract posterior samples of egg production
  E = post_subset(post, "^E_sep[", matrix = TRUE)

  # perform basic operations for one iteration -- for making dimension names later
  E_1 = array_format(E[1,])
  nor_1 = E_1[,k_3,o_nor,] + E_1[,k_4,o_nor,] + E_1[,k_5,o_nor,]
  hor_1 = E_1[,k_3,o_hor,] + E_1[,k_4,o_hor,] + E_1[,k_5,o_hor,]

  # function to perform the calculation for one MCMC sample
  g = function(i) {
    E_i = array_format(E[i,])
    list(
      nor = as.numeric(E_i[,k_3,o_nor,] + E_i[,k_4,o_nor,] + E_i[,k_5,o_nor,] + 1),
      hor = as.numeric(E_i[,k_3,o_hor,] + E_i[,k_4,o_hor,] + E_i[,k_5,o_hor,] + 1)
    )
  }

  # apply to each posterior sample
  out = lapply(1:nrow(E), g)

  # convert these to their own matrices for easier element construction
  nor_out = do.call(rbind, lapply(out, function(x) x$nor))
  hor_out = do.call(rbind, lapply(out, function(x) x$hor))

  # build element indices: the year
  y_ind = rep(1:nrow(nor_1), ncol(nor_1))

  # build element indices: the population
  j_ind = rep(1:ncol(nor_1), each = nrow(nor_1))

  # build element names
  colnames(nor_out) = paste0("E_org[", y_ind, ",", "1", ",", j_ind, "]")
  colnames(hor_out) = paste0("E_org[", y_ind, ",", "2", ",", j_ind, "]")

  # combine
  out = cbind(nor_out, hor_out)

  # drop out those that have NA values
  na_ind = which(!is.na(out[1,]))
  out[,na_ind]
}

# combine with the rest of the posterior samples
post = post_bind(post, f()); rm(f)
```

```{r add-E-per-Sa-origin}
f = function() {
  # extract posterior samples of egg production
  E_org = post_subset(post, "^E_org[", matrix = TRUE)
  Sa_org = post_subset(post, "^Sa_tot_org[", matrix = TRUE)

  # perform basic operations for one iteration -- for making dimension names later
  E_org_1 = array_format(E_org[1,])
  Sa_org_1 = array_format(Sa_org[1,])
  nor_1 = E_org_1[,o_nor,]/Sa_org_1[,o_nor,]
  hor_1 = E_org_1[,o_hor,]/Sa_org_1[,o_hor,]

  # function to perform the calculation for one MCMC sample
  g = function(i) {
    E_org_i = array_format(E_org[i,])
    Sa_org_i = array_format(Sa_org[i,])

    list(
      nor = as.numeric(E_org_i[,o_nor,]/Sa_org_i[,o_nor,]),
      hor = as.numeric(E_org_i[,o_hor,]/Sa_org_i[,o_hor,])
    )
  }

  # apply to each posterior sample
  out = lapply(1:nrow(E_org), g)

  # convert these to their own matrices for easier element construction
  nor_out = do.call(rbind, lapply(out, function(x) x$nor))
  hor_out = do.call(rbind, lapply(out, function(x) x$hor))

  # build element indices: the year
  y_ind = rep(1:nrow(nor_1), ncol(nor_1))

  # build element indices: the population
  j_ind = rep(1:ncol(nor_1), each = nrow(nor_1))

  # build element names
  colnames(nor_out) = paste0("E_per_Sa_org[", y_ind, ",", "1", ",", j_ind, "]")
  colnames(hor_out) = paste0("E_per_Sa_org[", y_ind, ",", "2", ",", j_ind, "]")

  # combine
  out = cbind(nor_out, hor_out)

  # drop out those that have NA values
  na_ind = which(!is.na(out[1,]))
  out[,na_ind]
}

# combine with the rest of the posterior samples
post = post_bind(post, f()); rm(f)
```

```{r add-Ma-tot}
f = function() {
  # extract posterior samples of smolt at LGR
  Ma = post_subset(post, "^Ma[", matrix = TRUE)

  # perform basic operations for one iteration -- for making dimension names later
  Ma_1 = array_format(Ma[1,])
  nor_1 = Ma_1[,i_fall,o_nor,] + Ma_1[,i_spring,o_nor,]
  hor_1 = Ma_1[,i_spring,o_hor,]

  # function to perform the calculation for one MCMC sample
  g = function(i) {
    Ma_i = array_format(Ma[i,])
    list(
      nor = as.numeric(Ma_i[,i_fall,o_nor,] + Ma_i[,i_spring,o_nor,]),
      hor = as.numeric(Ma_i[,i_spring,o_hor,])
    )
  }

  # apply to each posterior sample
  out = lapply(1:nrow(Ma), g)

  # convert these to their own matrices for easier element construction
  nor_out = do.call(rbind, lapply(out, function(x) x$nor))
  hor_out = do.call(rbind, lapply(out, function(x) x$hor))

  # build element indices: the year
  y_ind = rep(1:nrow(nor_1), ncol(nor_1))

  # build element indices: the population
  j_ind = rep(1:ncol(nor_1), each = nrow(nor_1))

  # build element names
  colnames(nor_out) = paste0("Ma_tot[", y_ind, ",", "1", ",", j_ind, "]")
  colnames(hor_out) = paste0("Ma_tot[", y_ind, ",", "2", ",", j_ind, "]")

  # combine
  out = cbind(nor_out, hor_out)

  # drop out those that have NA values
  na_ind = which(!is.na(out[1,]))
  out[,na_ind]
}

# combine with the rest of the posterior samples
post = post_bind(post, f()); rm(f)
```

```{r add-age-comp}
f = function() {
  # extract posterior samples of smolt at LGR
  Ra = post_subset(post, "^Ra[", matrix = TRUE)

  # perform basic operations for one iteration -- for making dimension names later
  Ra_1 = array_format(Ra[1,])
  nor_tot_1 = Ra_1[,k_3,o_nor,] + Ra_1[,k_4,o_nor,] + Ra_1[,k_5,o_nor,]
  hor_tot_1 = Ra_1[,k_3,o_hor,] + Ra_1[,k_4,o_hor,] + Ra_1[,k_5,o_hor,]
  p3_nor_1 = Ra_1[,k_3,o_nor,]/nor_tot_1
  p4_nor_1 = Ra_1[,k_4,o_nor,]/nor_tot_1
  p5_nor_1 = Ra_1[,k_5,o_nor,]/nor_tot_1
  p3_hor_1 = Ra_1[,k_3,o_hor,]/hor_tot_1
  p4_hor_1 = Ra_1[,k_4,o_hor,]/hor_tot_1
  p5_hor_1 = Ra_1[,k_5,o_hor,]/hor_tot_1
